Extending Morphological Chains with Supervised Learning and Cross-Language Features

### 2015-12-08 paper/paper.tex

\section{Semi-supervised Learning with Known Word Segmentations}
From known word segmentations, we can use these segmentations to reconstruct
the morphological chains that would lead to the correct segmentation of the word.

@@

>>>>

\section{Semi-supervised Learning with Known Word Segmentations}
In addition to maximizing the log-likelihood of the known wordlist,
we can also use explicit feedback regarding the correct segmentation of known words.
From these known segmentations, we can use these segmentations to reconstruct
the morphological chains that would lead to the correct segmentation of the word.

@@

\section{Using Cross-Language Features and Candidates}
Due to the simple nature of our parent candidate generation routine,
there are many cases in which the potential parent is not actually generated;
for example, the morphological parent of "feet" is the singular "foot";
however, there is no prefix or suffix that turns one into the other, and
therefore the parent for "feet" is not generated by our system.

However, other languages may not have such an irregular transformation
for the same words, for example in Turkish the corresponding translations
for "feet" and "foot" are "ayaklar" and "ayak". A properly trained Turkish
morphological parent model will correctly detect "ayak" as a parent of "ayaklar",
and can be used to suggest morphological parents in English after translation.

Since there are multiple possible morphological parents for a given word, and multiple
possible translations in either direction, this leads to many possible candidates for a given word,
we generate the set of possible parent candidates (from translation)
\begin{equation}
    C_2(w) = \bigcup_{w_t \in T_{ET}(w)}\left(\bigcup_{w_{tp} \in MP_T (w_t)} T_{TE}(w_{tp})\right)
\end{equation}
where $T_{ET}$ returns the set of possible Turkish translations
for an english word; $MP_T$ returns the set of possible parents for some Turkish word,
$T_{TE}$ returns the set of possible english translations for an english word,
and this potentially large set of candidates is pruned with heuristics judging
how similar the candidate is to the original word.
